itle: "Report for Project One: Nearest Neighbors"
author: "Kaitlyn Grubb"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Report for Project One: Nearest Neighbors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r data}
data.name.vec <- c(
  "spam",
  "SAheart",
  "zip.train",
  "prostate",
  "ozone")
data.list <- list()
library(ElemStatLearn)
for(data.name in data.name.vec)
{
  data(list = data.name, package="ElemStatLearn")
  data.list[[data.name]] <- get(data.name)
}
str(data.list)

is.binary <- ElemStatLearn::zip.train[,1] %in% c(0,1)

data.list <- list(
  spam=list(
    label.vec=ifelse(ElemStatLearn::spam$spam=="spam", 1, 0),
    feature.mat=as.matrix(ElemStatLearn::spam[, -ncol(ElemStatLearn::spam)])),
  zip.train=list(
    label.vec=ElemStatLearn::zip.train[is.binary,1],
    feature.mat=ElemStatLearn::zip.train[is.binary,-1])
)


n.folds <- 5
resultsList <- list()
for(data.name in names(data.list))
{
  one.data.set <- data.list[[data.name]]
  set.seed(1)
  fold.vec <- sample(rep(1:n.folds, l=nrow(one.data.set$feature.mat)))
    #NearestNeighborsCV(one.data.set$feature.mat,   one.data.set$label.vec)
  for(test.fold in 1:(n.folds))
  {
    is.train <- fold.vec != test.fold
    fit <- NearestNeighborsCV(one.data.set$feature.mat[is.train],   one.data.set$label.vec[is.train])
    pred.vec <- fit$predict(one.data.set$feature.mat[!is.train])
    ## compute test error of pred vec with respect to one data.set$label[!is.train]
    
    ### MY CODE TO COMPUTE ERROR
    error = 1/test.fold 
    
    resultsList[{paste(data.name, test.fold)}] <- # save your results
  }
}
```

## Data set 1: spam

### Matrix of loss values

```{r}
#print out and/or plot the matrix.


```

comment on difference between NN and baseline.

### Train/validation loss plot

```{r}
#plot the two loss functions.


```

What is the optimal number of neighbors?

## Data set 2: SAheart

### Matrix of loss values

```{r}
#print out and/or plot the matrix.


```

comment on difference between NN and baseline.

### Train/validation loss plot

```{r}
#plot the two loss functions.


```

What is the optimal number of neighbors?

## Data set 3: zip.train

### Matrix of loss values

```{r}
#print out and/or plot the matrix.


```

comment on difference between NN and baseline.

### Train/validation loss plot

```{r}
#plot the two loss functions.


```

What is the optimal number of neighbors?

## Data set 4: prostate 

### Matrix of loss values

```{r}
#print out and/or plot the matrix.


```

comment on difference between NN and baseline.

### Train/validation loss plot

```{r}
#plot the two loss functions.


```

What is the optimal number of neighbors?

## Data set 4: ozone 

### Matrix of loss values

```{r}
#print out and/or plot the matrix.


```

comment on difference between NN and baseline.

### Train/validation loss plot

```{r}
#plot the two loss functions.


```

What is the optimal number of neighbors?